Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-03-26 main.Rmd
Fixed table justification

\begin{table}[ht]
\begin{center}
\begin{tabular}{lr@{~}lr@{~}r}
\hline
circular granularity && expression  && period length\\
\hline
minute-of-hour & $C_1$ & $= L_1(z \mod 60)$  & $P_1 = $&$60$ \\
minute-of-day & $C_2$ & $= L_2(z \mod 60*24)$  & $P_2=$&$`r 60*24`$\\
hour-of-day & $C_3$ & $= L_3(\lfloor z/60\rfloor\mod 24)$  & $P_3 =$&$24$ \\
hour-of-week & $C_4$ & $= L_4(\lfloor z/60\rfloor\mod 24*7)$  & $P_4=$&$`r 24*7`$\\
day-of-week & $C_5$ & $= L_5(\lfloor z/24*60\rfloor \mod 7)$  & $P_5=$&$7$\\
\bottomrule
\end{tabular}
\end{center}
\caption{Examples of circular granularities with bottom granularity minutes. Circular granularity $C_i$ relates two linear granularities one of which groups periodically into the other with regular mapping and $P_i$ represents the period length. Circular granularities could be expressed using modular arithmetic due to their regular mapping. }
\label{tab:definitions}
\end{table}

>>>>

\begin{table}[ht]
\begin{center}
\begin{tabular}{lll}
\hline
circular granularity & expression & period length \\
\hline
minute-of-hour                               &
  $C_1 = L_1(z \mod 60)$                     &
  $P_1 = \phantom{99}60$ \\
minute-of-day                                &
  $C_2 = L_2(z \mod 60*24)$                  &
  $P_2= `r 60*24`$\\
hour-of-day                                  &
  $C_3 = L_3(\lfloor z/60\rfloor\mod 24)$    &
  $P_3 = \phantom{99}24$ \\
hour-of-week                                 &
  $C_4 = L_4(\lfloor z/60\rfloor\mod 24*7)$  &
  $P_4= \phantom{9}`r 24*7`$\\
day-of-week                                  &
  $C_5 = L_5(\lfloor z/24*60\rfloor \mod 7)$ &
  $P_5= \phantom{999}7$\\
\bottomrule
\end{tabular}
\end{center}
\caption{Examples of circular granularities with bottom granularity minutes. Circular granularity $C_i$ relates two linear granularities one of which groups periodically into the other with regular mapping and $P_i$ represents the period length. Circular granularities could be expressed using modular arithmetic due to their regular mapping. }
\label{tab:definitions}
\end{table}
